Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-07 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

@@

In a study investigating the formation of human immunodeficiency virus (HIV) VLPs the correlated
SICM-fluorescence confocal microscopy (SICM-FCM) was used to investigate topography changes
together with die distribution of fluorescently labeled viral proteins like Gag or Viral Protein R 
(Vpr) \cite{Bednarska2020}. In contrast of investigating the virus formation with total internal 
reflection fluorescence (TIRF) microscopy \cite{Jouvenet2008} the upside (Oberseite?) of the cells 
were investigated. The release of VLPs from the upside can be a lot faster, than the release times 
that were known from TIRF measurements and difference between different cell types and labeled 
virus proteins were found \cite{Bednarska2020}.

@@

@@

Beside these more or less \emph{direct} combinations and correlations, which are displaying images 
obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
correlations exist. They are showing images under comparable conditions and extent the 
investigation to aspects, which could not be obtained by using one technique alone. Such 
\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
Nevertheless is it important to mention, that they could just giving hints of correlations, it 
is not directly comparable with investigations of both in the same cell.

>>>>

In a study investigating the formation of human immunodeficiency virus (HIV) virus-like particles 
(VLPs) the correlated SICM-fluorescence confocal microscopy (SICM-FCM) was used to investigate 
topography changes together with die distribution of fluorescently labeled viral proteins like Gag 
or Viral Protein R (Vpr) \cite{Bednarska2020}. In contrast of investigating the virus formation 
with total internal reflection fluorescence (TIRF) microscopy \cite{Jouvenet2008} the upside 
(Oberseite?) of the cells were investigated. The release of VLPs from the upside can be a lot 
faster, than the release times that were known from TIRF measurements and difference between 
different cell types and labeled virus proteins were found \cite{Bednarska2020}.

\subsection{\emph{Indirect} combination of SICM and FM}

Beside \emph{direct} combinations in one instrument and correlations, which are displaying images 
obtained by SICM and fluorescence microscopy of the same cell/same region, also \emph{indirect} 
correlations exist. They are showing images under comparable conditions and extent the 
investigation to aspects, which could not be obtained by using one technique alone. Such 
\emph{indirect} correlations were used for investigating the uptake of nanotubes \cite{Lee2013}, 
nanoparticles \cite{Gesper2017} or for investigating healthy and failing myocytes \cite{Lyon2009}. 
Nevertheless is it important to mention, that they could just giving hints of correlations, it 
is not directly comparable with investigations of both in the same cell.

@@

@@

\subsection{Nanoinjection of fluorescently labeled molecules}

@@
